%-------------------------
% Resume in Latex
% Author : Caleb Tracey
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Caleb Tracey} \\ \vspace{1pt}
    \small 207-332-0452 $|$ Portland, ME \\ \vspace{1pt}
    \href{mailto:x@x.com}{\underline{caleb.tracey@gmail.com}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/caleb-tracey/}} $|$
    \href{https://github.com/...}{\underline{github.com/calebtracey}}
\end{center}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Full Stack Engineer I}{November 2021 -- Present}
      {Centene Corporation}{Portland, ME (Remote)}
      \resumeItemListStart
        \resumeItem{Implemented GraphQL on three flagship products, reducing response times by 20\% and enhancing user experience and system performance.}
        \resumeItem{Led conversion of three legacy Java endpoints to Go APIs, ensuring seamless deployment to both test and production Kubernetes clusters using GitLab CI pipeline. Collaborated closely with product owners to prioritize scalability and maintainability over updating legacy Java code.}
        \resumeItem{Assisted in refactoring a customer-specific GraphQL monolith into tailored federated APIs using Apollo Federation to optimize service architecture and performance.}
        \resumeItem{Utilized Go’s package-based design to modularize business logic across microservices, reducing repository sizes by 20-40\% and facilitating tag-based development to eliminate duplicate code and mitigate regression issues.}
        \resumeItem{Modernized four outdated Go repositories using the facade design pattern, ensuring long-term maintainability, clarity, and raising code coverage above 90\%}
        \resumeItem{Designed and implemented GitLab CI pipeline to migrate two legacy Java APIs from Linux Boxes to Kubernetes clusters, ensuring zero downtime through streamlined deployments with Helm and Docker. Standardized deployment procedures for improved scalability and efficiency.}
        \resumeItem{Detected data races within concurrent codebases using Go’s testing library and Pprof profiling tool to enhance code reliability and performance.}
        \resumeItem{Demonstrate strong collaboration skills by effectively partnering with external teams and clients to address critical issues across test and production environments, maintaining 100\% service delivery.}
        \resumeItem{Coordinate and supervise rotational deployments every 4–6 weeks, ensuring seamless documentation, task delegation, and proactive engagement with downstream customers.}
        \resumeItem{Assisted Business Technologies Solutions initiative by conducting presentations on remote workplace etiquette for new hires and interns, achieving an NPS of 50.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages and Frameworks}{: Go, Java, SQL, TypeScript/JavaScript, Spring, React} \\
     \textbf{Developer Tools}{: GraphQL, Kubernetes, Docker, Helm, MongoDB, Dynatrace,
     Rancher, Grafana, Kibana, Pprof} \\
     \textbf{Technologies}{:  Git, Gitlab CI/CD, Jira, Confluence}
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{ConfigConnect} $|$ \emph{Go}}{Jul 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Designed and developed a Go package for effortless API configuration and initialization. This package seamlessly reads authentication and connection details from a YAML config file, streamlining connectivity with upstream services and databases. It produces a configured Go struct with initialized methods for accessing these services.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Ultrasound App UI/API} $|$ \emph{React, TS, Spring Boot, Maven, MongoDB, Docker}}{May 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Architected, designed, and developed the React/TypeScript front-end for a training application utilized by a fellowship program at a local hospital, demonstrating proficiency in architectural considerations and user interface implementation.}
            \resumeItem{Developed a high-performance REST API using Spring Boot, optimizing the MongoDB data model for efficient storage and back-end parsing of a large-scale collection of 3000+ MP4 files.}
            \resumeItem{Utilized Spring Security to implement robust JWT authentication and role-based access control, ensuring secure and controlled access to the application.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd




%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Southern Maine Community College}{South Portland, ME}
      {Associate Degree in Computer Science}{Jan. 2020 -- May 2021}
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
